Artin Group Presentations Arising from Cluster Algebras

### 2014-08-01 Paper.tex
Minor Edit
small edits

\todo{do we define $m_{ij}'$ somewhere?}

@@

We prove Proposition \ref{prop:ti_relations} by showing that that the elements $\varphi(r_i)\in A_\Gamma$ satisfy the $(R2^\prime)$ and $(R3^\prime)$ relations in $A_{\Gamma^\prime}$.  The proof that the $\varphi(r_i)$ satisfy these relations is divided among Lemmas \ref{lem:r2a_relations}, \ref{lem:r2b_relations}, and \ref{lem:r3_relations}.  Throughout the proofs we write $t_i = \varphi(r_i)$ for convenience.

@@

\begin{proof}
The possibilities for the subdiagram induced by $i$, $j$, and $k$ are enumerated in Corollary \ref{local_three_picture}.  We show that $t_i$ and $t_j$ satisfy the $(R2^\prime)$ relations by checking each case.  Within each case, subcase $(i)$ is when the subdiagram of $\Gamma$ is the diagram on the left in the figure in Corollary \ref{local_three_picture}, and subcase $(ii)$ is when the subdiagram of $\Gamma$ is the diagram on the right in the figure in Corollary \ref{local_three_picture}.

@@

\begin{lem}\label{lem:r3_relations}
The elements $t_i$ satisfy the $(R3^\prime)$ relations in $\Gamma^\prime$.
\end{lem}

\begin{proof}
We know that every chordless cycle in $\Gamma'$ arises from a subdiagram of $\Gamma$ in the form of one of the cases of Lemma \ref{lem:chordless_cycles}, so we simply need to check that a cycle relation holds in each case.  We follow the labeling of the vertices used in Lemma \ref{lem:chordless_cycles}.  We denote by $r^\prime(m,n)$ the expression given by replacing the generators $r_i$ in the corresponding expression $r(m,n)$ in $A_{\Gamma^\prime}$ with $t_i$.  When helpful we note uses of $(R3)$ relations in $A_\Gamma$ by referencing the particular cycle relation used next to the manipulation.

\begin{enumerate}[a)]
\item We have $t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_1s_3 = s_3s_1 = t_2^{-1}t_3t_2t_1$, hence $r^\prime(1,2) = e$.

\item We have $ t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_1s_3 = s_3s_1 = t_2^{-1}t_3t_2t_1$, hence $r^\prime(1,2) = e$.

\item We have $t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_3s_1 = t_2^{-1}t_3t_2t_1$, hence $r^\prime(1,2) = e$.

\item We have
\begin{align*}
s_2^{-1}r^\prime(3,1)s_2 &= s_2^{-1}t_3t_1^{-1}t_2t_1t_3^{-1}t_1^{-1}s_2^{-1}t_1s_2\\
&= s_3\underline{s_2^{-1}s_1^{-1}s_2s_1s_2}s_3^{-1}\underline{s_2^{-1}s_1^{-1}s_2^{-1}s_1s_2}\\
&= s_3s_1\underline{s_2s_1^{-1}s_3^{-1}s_1}s_2^{-1}s_1^{-1}\\
&= s_3s_1s_1^{-1}s_3^{-1}s_1s_2s_2^{-1}s_1^{-1} &r(2,1)\\
&= e
\end{align*}

\noindent Hence $r^\prime(3,1) = e$.

\item We have
\begin{align*}
t_1t_2^{-1}t_3^{-1}t_4t_3t_2 &= (s_1s_2^{-1}s_1^{-1}s_1s_2s_1^{-1})s_1s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}\underline{s_1s_2s_1s_2^{-1}s_1^{-1}}s_3^{-1}s_4s_3s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}\underline{s_2s_3^{-1}s_4s_3}s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3\underline{s_2s_1s_2s_1^{-1}} &r(2,3)\\
&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}s_1\\
&= t_2^{-1}t_3^{-1}t_4t_3t_2t_1\\
\end{align*}

\noindent Hence $r^\prime(1,2) = e$.

\item We have
\begin{align*}
t_1t_2^{-1}t_3^{-1}t_4t_3t_2 &= s_1\underline{s_2^{-1}s_2}s_3^{-1}\underline{s_2^{-1}s_4s_2}s_3 \underline{s_2^{-1}s_2}\\
&= s_1s_3^{-1}s_4s_3\\
&= s_3^{-1}s_4s_3s_1 &r(1,3)\\
&= (s_2^{-1}s_2)s_3^{-1}(s_2^{-1}\underline{s_2)s_4(s_2^{-1}}s_2)s_3(s_2^{-1}s_2s_1\\
&= s_2^{-1}s_2s_3^{-1}s_2^{-1}s_4s_2s_3s_2^{-1}s_2s_1\\
&= t_2^{-1}t_3^{-1}t_4t_3t_2t_1\\
\end{align*}

\noindent Hence $r^\prime(1,2) = e$.

\item We have
\begin{align*}
r^\prime(3,4) &= t_3t_4^{-1}t_2t_4t_3^{-1}t_4^{-1}t_2^{-1}t_4\\
&= \underline{s_3s_1}s_4^{-1}s_1^{-1}s_2s_1s_4\underline{s_1^{-1}s_3^{-1}s_1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4s_1^{-1}\\
&= s_1\underline{s_3s_4^{-1}s_1^{-1}s_2s_1s_4s_3^{-1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4}s_1^{-1}\\
&= s_1r(3,4)s_1^{-1}\\
&= s_1s_1^{-1}\\
&= e\\
\end{align*}

\item We have
\begin{align*}
t_3t_4^{-1}t_1t_4 &= s_3s_4^{-1}\underline{s_2s_1s_2^{-1}}s_4\\
&= s_3s_4^{-1}s_1^{-1}s_2s_1s_4\\
&= s_4^{-1}\underline{s_1^{-1}s_2s_1}s_4s_3 &r(3,4)\\
&= s_4^{-1}s_2s_1s_2^{-1}s_4s_3\\
&= t_4^{-1}t_1t_4t_3\\
\end{align*}

\noindent Hence $r^\prime(3,4) = e$.

\item We have
\begin{align*}
&r^\prime(1,2)\\
&= t_1t_2^{-1}t_3^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1^{-1}t_2^{-1}\cdots t_{h-1}^{-1}t_h^{-1}t_{h-1}\cdots t_2\\
&= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_hs_k^{-1}}s_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_h^{-1}s_k^{-1}}s_{h-1}\cdots s_2\\
&= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_ks_hs_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_k^{-1}s_hs_{h-1}\cdots s_2\\
&= r(1,2)\\
&= e\\
\end{align*}

\item Here $s_k$ commutes with $s_i$ for all $i\ne 1,h$, so we have
\begin{align*}
& r^\prime(h,1)\\
&= t_ht_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}t_{h-2}\cdots t_1t_kt_h^{-1}t_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}^{-1}t_{h-2}\cdots t_2t_1t_k\\
&= s_h\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots \underline{s_k}s_1\underline{s_k^{-1}s_k}s_h^{-1}\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}^{-1}s_{h-2}\cdots s_2 \underline{s_k}s_1\underline{s_k^{-1}s_k}\\
&= s_hs_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots s_2s_1s_h^{-1}s_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}^{-1}s_{h-2}\cdots s_2s_1\\
&= r(h,1)\\
&= e\\
\end{align*}

@@

\begin{align*}
t_1t_2^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2 &= s_1s_2^{-1}\cdots s_{h-1}^{-1}s_ks_hs_k^{-1}s_{h-1}\cdots s_2\\
&= s_k\underline{s_1s_2^{-1}\cdots s_{h-1}^{-1}s_hs_{h-1}\cdots s_2}s_k^{-1}\\
&= s_ks_2^{-1}\cdots s_{h-1}^{-1}s_hs_{h-1}\cdots s_2s_1s_k^{-1} &r(1,2)\\
&= s_2^{-1}\cdots s_{h-1}^{-1}s_ks_hs_k^{-1}s_{h-1}\cdots s_2s_1\\
&= t_2^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1\\
\end{align*}

\noindent Hence $r^\prime(1,2) = e$.
\end{enumerate}
\end{proof}

\begin{proof}[Proof of Proposition \ref{prop:ti_relations}]
Lemma \ref{lem:r2a_relations} and Lemma \ref{lem:r2b_relations} show that the elements $t_i$ satisfy the $(R2^\prime)$ relations for $A_{\Gamma^\prime}$. Lemma \ref{lem:r3_relations} shows that they satisfy the $(R3^\prime)$ relations. Since these are all of the relations defining $A_{\Gamma^\prime}$, it follows that $\varphi$ defines a group homomorphism $A_{\Gamma^\prime}\rightarrow A_\Gamma$.
\end{proof}

>>>>

@@

We prove Proposition \ref{prop:ti_relations} by showing that that the elements $\varphi(r_i)\in A_\Gamma$ satisfy the $(T2^\prime)$ and $(T3^\prime)$ relations in $A_{\Gamma^\prime}$.  The proof that the $\varphi(r_i)$ satisfy these relations is divided among Lemmas \ref{lem:r2a_relations}, \ref{lem:r2b_relations}, and \ref{lem:r3_relations}.  Throughout the proofs we write $t_i = \varphi(r_i)$ and $m_{ij}^\prime$ for the weight of the edge between $i$ and $j$ in $\Gamma^\prime$.

@@

\begin{proof}
The possibilities for the subdiagram induced by $i$, $j$, and $k$ are enumerated in Corollary \ref{local_three_picture}.  We show that $t_i$ and $t_j$ satisfy the $(T2^\prime)$ relations by checking each case.  Within each case, subcase $(i)$ is when the subdiagram of $\Gamma$ is the diagram on the left in the figure in Corollary \ref{local_three_picture}, and subcase $(ii)$ is when the subdiagram of $\Gamma$ is the diagram on the right in the figure in Corollary \ref{local_three_picture}.

@@

\begin{lem}\label{lem:r3_relations}
The elements $t_i$ satisfy the $(T3^\prime)$ relations in $\Gamma^\prime$.
\end{lem}

\begin{proof}
We know that every chordless cycle in $\Gamma'$ arises from a subdiagram of $\Gamma$ in the form of one of the cases of Lemma \ref{lem:chordless_cycles}, so we simply need to check that a cycle relation holds in each case.  We follow the labeling of the vertices used in Lemma \ref{lem:chordless_cycles}.  We denote by $t^\prime(m,n)$ the expression given by replacing the generators $r_i$ in the corresponding expression $t(m,n)$ in $A_{\Gamma^\prime}$ with $t_i$.  When helpful we note uses of $(T3)$ relations in $A_\Gamma$ by referencing the particular cycle relation used next to the manipulation.

\begin{enumerate}[a)]
\item We have $t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_1s_3 = s_3s_1 = t_2^{-1}t_3t_2t_1$, hence $t^\prime(1,2) = e$.

\item We have $ t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_1s_3 = s_3s_1 = t_2^{-1}t_3t_2t_1$, hence $t^\prime(1,2) = e$.

\item We have $t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_3s_1 = t_2^{-1}t_3t_2t_1$, hence $t^\prime(1,2) = e$.

\item We have
\begin{align*}
s_2^{-1}t^\prime(3,1)s_2 &= s_2^{-1}t_3t_1^{-1}t_2t_1t_3^{-1}t_1^{-1}s_2^{-1}t_1s_2\\
&= s_3\underline{s_2^{-1}s_1^{-1}s_2s_1s_2}s_3^{-1}\underline{s_2^{-1}s_1^{-1}s_2^{-1}s_1s_2}\\
&= s_3s_1\underline{s_2s_1^{-1}s_3^{-1}s_1}s_2^{-1}s_1^{-1}\\
&= s_3s_1s_1^{-1}s_3^{-1}s_1s_2s_2^{-1}s_1^{-1} &t(2,1)\\
&= e
\end{align*}

\noindent Hence $t^\prime(3,1) = e$.

\item We have
\begin{align*}
t_1t_2^{-1}t_3^{-1}t_4t_3t_2 &= (s_1s_2^{-1}s_1^{-1}s_1s_2s_1^{-1})s_1s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}\underline{s_1s_2s_1s_2^{-1}s_1^{-1}}s_3^{-1}s_4s_3s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}\underline{s_2s_3^{-1}s_4s_3}s_1s_2s_1^{-1}\\
&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3\underline{s_2s_1s_2s_1^{-1}} &t(2,3)\\
&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}s_1\\
&= t_2^{-1}t_3^{-1}t_4t_3t_2t_1\\
\end{align*}

\noindent Hence $t^\prime(1,2) = e$.

\item We have
\begin{align*}
t_1t_2^{-1}t_3^{-1}t_4t_3t_2 &= s_1\underline{s_2^{-1}s_2}s_3^{-1}\underline{s_2^{-1}s_4s_2}s_3 \underline{s_2^{-1}s_2}\\
&= s_1s_3^{-1}s_4s_3\\
&= s_3^{-1}s_4s_3s_1 &t(1,3)\\
&= (s_2^{-1}s_2)s_3^{-1}(s_2^{-1}\underline{s_2)s_4(s_2^{-1}}s_2)s_3(s_2^{-1}s_2s_1\\
&= s_2^{-1}s_2s_3^{-1}s_2^{-1}s_4s_2s_3s_2^{-1}s_2s_1\\
&= t_2^{-1}t_3^{-1}t_4t_3t_2t_1\\
\end{align*}

\noindent Hence $t^\prime(1,2) = e$.

\item We have
\begin{align*}
t^\prime(3,4) &= t_3t_4^{-1}t_2t_4t_3^{-1}t_4^{-1}t_2^{-1}t_4\\
&= \underline{s_3s_1}s_4^{-1}s_1^{-1}s_2s_1s_4\underline{s_1^{-1}s_3^{-1}s_1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4s_1^{-1}\\
&= s_1\underline{s_3s_4^{-1}s_1^{-1}s_2s_1s_4s_3^{-1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4}s_1^{-1}\\
&= s_1t(3,4)s_1^{-1}\\
&= s_1s_1^{-1}\\
&= e\\
\end{align*}

\item We have
\begin{align*}
t_3t_4^{-1}t_1t_4 &= s_3s_4^{-1}\underline{s_2s_1s_2^{-1}}s_4\\
&= s_3s_4^{-1}s_1^{-1}s_2s_1s_4\\
&= s_4^{-1}\underline{s_1^{-1}s_2s_1}s_4s_3 &t(3,4)\\
&= s_4^{-1}s_2s_1s_2^{-1}s_4s_3\\
&= t_4^{-1}t_1t_4t_3\\
\end{align*}

\noindent Hence $t^\prime(3,4) = e$.

\item We have
\begin{align*}
&t^\prime(1,2)\\
&= t_1t_2^{-1}t_3^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1^{-1}t_2^{-1}\cdots t_{h-1}^{-1}t_h^{-1}t_{h-1}\cdots t_2\\
&= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_hs_k^{-1}}s_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_h^{-1}s_k^{-1}}s_{h-1}\cdots s_2\\
&= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_ks_hs_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_k^{-1}s_hs_{h-1}\cdots s_2\\
&= t(1,2)\\
&= e\\
\end{align*}

\item Here $s_k$ commutes with $s_i$ for all $i\ne 1,h$, so we have
\begin{align*}
& t^\prime(h,1)\\
&= t_ht_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}t_{h-2}\cdots t_1t_kt_h^{-1}t_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}^{-1}t_{h-2}\cdots t_2t_1t_k\\
&= s_h\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots \underline{s_k}s_1\underline{s_k^{-1}s_k}s_h^{-1}\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}^{-1}s_{h-2}\cdots s_2 \underline{s_k}s_1\underline{s_k^{-1}s_k}\\
&= s_hs_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots s_2s_1s_h^{-1}s_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}^{-1}s_{h-2}\cdots s_2s_1\\
&= t(h,1)\\
&= e\\
\end{align*}

@@

\begin{align*}
t_1t_2^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2 &= s_1s_2^{-1}\cdots s_{h-1}^{-1}s_ks_hs_k^{-1}s_{h-1}\cdots s_2\\
&= s_k\underline{s_1s_2^{-1}\cdots s_{h-1}^{-1}s_hs_{h-1}\cdots s_2}s_k^{-1}\\
&= s_ks_2^{-1}\cdots s_{h-1}^{-1}s_hs_{h-1}\cdots s_2s_1s_k^{-1} &t(1,2)\\
&= s_2^{-1}\cdots s_{h-1}^{-1}s_ks_hs_k^{-1}s_{h-1}\cdots s_2s_1\\
&= t_2^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1\\
\end{align*}

\noindent Hence $t^\prime(1,2) = e$.
\end{enumerate}
\end{proof}

\begin{proof}[Proof of Proposition \ref{prop:ti_relations}]
Lemma \ref{lem:r2a_relations} and Lemma \ref{lem:r2b_relations} show that the elements $t_i$ satisfy the $(T2^\prime)$ relations for $A_{\Gamma^\prime}$. Lemma \ref{lem:r3_relations} shows that they satisfy the $(T3^\prime)$ relations. Since these are all of the relations defining $A_{\Gamma^\prime}$, it follows that $\varphi$ defines a group homomorphism $A_{\Gamma^\prime}\rightarrow A_\Gamma$.
\end{proof}
